From Object Classification to Naming: Modeling Entry-level Names for Real-world Objects

### 2019-12-10 papers/ACL2020/acl2020_main.tex
shortening -0.5 page
[ACL2020] main

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{color, colortbl}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[latin1]{inputenc}
\usepackage{latexsym}
\usepackage{multirow}
\usepackage{times}
\usepackage{url}
\usepackage{xcolor}
\usepackage{xspace}

@@

\begin{document}
\maketitle
\begin{abstract}
Object detection and image classification models from Computer Vision are typically trained towards predicting labels of objects. 
Our goal is to extend such models to entry-level naming, where the task is to predict the natural name of an object that most humans would choose, instead of an \arbitrary name chosen by a single annotator. 
Based on large-scale, thoroughly verified object naming data from many annotators, we conduct an extensive analysis of the ability of object detection and classification models to account for entry-level object naming.
We show that standard object classification models ``spontaneously'' learn good entry-level names and perform better
on predicting entry-level than \arbitrary names, despite being trained on  \arbitrary names.
We further fine-tune these models via transfer learning and systematically vary their training vocabulary.
\sz{something ...}
\end{abstract}

@@

\section{ManyNames: A Source for Entry-Level Names}
\label{sec:manynames}
%\cs{to add: footnote saying that the \mn data will be published upon acceptance of the paper.}
\input{manynames}

>>>>

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{color, colortbl}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[latin1]{inputenc}
\usepackage{latexsym}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage{times}
\usepackage{url}
\usepackage{xcolor}
\usepackage{xspace}

@@

\begin{document}
\maketitle
\begin{abstract}
Object detection and image classification models from Computer Vision are typically trained towards predicting labels of objects. 
Our goal is to extend such models to entry-level naming, where the task is to predict the natural name of an object that most humans would choose, instead of an \arbitrary name chosen by at best a few annotators. 
Based on large-scale, thoroughly verified object naming data from many annotators, we conduct an extensive analysis of the ability of object detection and classification models to account for entry-level object naming.
We show that standard object classification models ``spontaneously'' learn good entry-level names and perform better
on predicting entry-level than \arbitrary names, despite being trained on the latter, and that we can use transfer learning to train entry-level classifiers on the naming data. 
Our analyses also reveal the limitations of modeling human naming behavior with proxy data of the true situation in which the phenomenon occurs.  
%and systematically vary their training vocabulary. \cs{no diffs here with our setup of entry-levels only}
\sz{something ...}
\end{abstract}

@@

\section{Adequacy and Errors in ManyNames}
\label{sec:manynames}
%\cs{to add: footnote saying that the \mn data will be published upon acceptance of the paper.}
\input{manynames}
